---
title: "SWORK 881 week02"
author: "Mele'ana 'Akolo"
date: "02/01/2022"
output: html_document
---

# load libraries
```{r setup, include=FALSE}
library(tidyverse)
library(tidymodels)


```


# Data
```{r}
# load data
data.01<- read_csv("Data/LHS_exercise_01272022.csv")

#how many observations and variables? 
#268 observations; 8 variables

```
#how many observations and variables? 
#268 observations; 8 variables
```{r}
# create a new variable called `depression` by summing all ptsd variables. Use tidy approach
data.02<- data.01%>%
  select(ptsd1_1, ptsd2_1, ptsd3_1, ptsd4_1, age, sex, education)%>%
  mutate(depression_score = rowSums(across(ptsd1_1:ptsd4_1), na.rm=T),
     ptsd_mean = rowMeans(across(ptsd1_1:ptsd4_1), na.rm=T))    

```


```{r}
#run simple descriptive statistics for all variables

fit.1 <- lm(depression_score ~age+education+factor(sex),       
            data=data.02)

summary (fit.1)


```

#DESCRIBE THE DATA BRIEFLY HERE
#I have an additional variable called 'depression' score with the mean 

# Model and Visualization
> What is the effect of `age`, `sex`, and `education` on `depression score`? 
#Age has a significant effect on depression score but education and sex have no significant effect on depression score.

Create a linear regression model that answers the question above. Print the results of the output and model diagnostics.
```{r}
# lm
lm(depression_score ~age+factor(sex)+education,
            data=data.02)



```


```{r}
# model diagnostics
par(mfrow=c(2,2))
plot (fit.1)

```


```{r}
# use ggplot to plot histogram of residuals (use 20 bins)
ggplot(fit.1,
       aes(fit.1$residuals))+
  geom_histogram(bins=20)

```

# Discussion of Results

Describe and interpret your results, including any statistical information you believe important: Based on the histogram the distribution appears to be skewed to the right where as age increases depression score also increases.

